\papertitle

### 2012-10-11 manuscript.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO ryan
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.

\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird Ornithopter MAV}
\label{fig:h2bird}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
% ryan

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/process_flow.pdf}
\caption{Process flow diagram for the cooperative control system.}
\label{fig:process_flow}
\end{figure}

@@

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

We determined the backwards reachable set of initial states for successful
window traversal both geometrically and in simulation. The results are shown
in Figure~\ref{fig:feasible_set}. For the initial conditions, we used a
spatial grid of 0.05 meter increments within the camera viewing region and an
initial angular position perpendicular to the window plane. The geometrically
infeasible region is indicated in blue and was computed using the minimum
turning radius and simple geometry. Both the regions in red and blue indicate
the infeasible region determined in simulation. We simulated the turning
model, described in Section~\ref{sec:flight_control}, with a PID controller
steering the system to the center of the window as the input. The infeasible
region calculated in simulation is a superset of the geometrically infeasible
region. The simulation is more realistic as the rotational damping during the
turn and the on-board PID controller cause the real system to react to inputs
at a non-constant angular velocity.
\\
To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from the window along the
edges of the camera image frame. We began each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.
\\
For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 79\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending upon the PID
tuning and the distance from the camera. Tracking noise can also cause the
window navigation to fail.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
\\
Autonomous control of flapping winged MAVs is a complex undertaking, because
of the nonlinear flight dynamics and underactuation of the system due to size
constraints. Many of the methods for controlling these platforms make
extensive use of GPS in outdoor environments [CITATIONS]. When operating
indoors, using GPS to estimate the pose of the MAV is not reliable. The
periodic motion and payload limits on MAVs make on-board sensing difficult, so
external sensing and multi-agent cooperative control schemes are apt
solutions.
\\
Many of the control laws that previous researches have developed from the dynamic models of flapping-winged flight are computationally complex and require powerful on-board computing [CITATIONS]. In our work, we develop a simpler, less computationally intensive method of control for accomplishing navigation through a narrow passage.
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird Ornithopter MAV}
\label{fig:h2bird}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%TODO ryan

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/process_flow.pdf}
\caption{Overview of the cooperative control system.}
\label{fig:process_flow}
\end{figure}

@@

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{figure}

We determined the backwards reachable set of initial states for successful
window traversal both geometrically and in simulation. The results are shown
in Figure~\ref{fig:feasible_set}. For the initial conditions, we used a
spatial grid of 0.05 meter increments within the camera viewing region and an
initial angular position perpendicular to the window plane. The geometrically
infeasible region is indicated in blue and was computed using the minimum
turning radius and simple geometry. Both the regions in red and blue indicate
the infeasible region determined in simulation. We ran a simulation on a
motion model similar to Dubin's car in ~\cite{lavalle:planning}, with the
angular heading as the input rather than the angular velocity. We used the
turning model, described in Section~\ref{sec:flight_control}, as the input to
the motion model, with a PID controller steering the entire system to the
center of the window as the input to the tuning model. The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.
\\
To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from the window along the
edges of the camera image frame. We began each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.
\\
For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 79\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending upon the PID
tuning and the distance from the camera. Tracking noise can also cause the
window navigation to fail.
